---
title: "An efficient computation of Dempster-Shafer theory of evidence based on native GPU implementation 💻"
subtitle: "<br/>with xaringan"
author: "<b>Noelia Rico</b><sup>1</sup>, Luigi Troiano<sup>2</sup>, Irene Díaz<sup>1</sup>"
institute: "<br/> <sup>1</sup>Department of Computer Science, University of Oviedo, Spain <br/> <sup>2</sup>University of Salerno, Italy"
email: "otra cosa"
output:
  xaringan::moon_reader:
    css: ["unimode.css", "fonts-unimode.css"]
   
---

```{r xaringanExtra, echo = FALSE}
# meter en css para una apariencia mas latex
 #nature:
      #slideNumberFormat: "%current%/%total%"
xaringanExtra::use_logo("logo.png")
xaringanExtra::use_progress_bar(color = "purple", location = "bottom")
```


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
# library(xaringanthemer)
# style_duo_accent(
#   primary_color = "#EBE9FD",
#   secondary_color = "#FF961C",
#   inverse_header_color = "#FFFFFF"
# )
```

background-image: url(https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg)

???

Image credit: [Wikimedia Commons](https://commons.wikimedia.org/wiki/File:Sharingan_triple.svg)

---


---

# Basic functions: Belief and Plausibility

$$Bel(A)=\sum_{S\subseteq A} m(S)$$

$$Pl(A)=\sum_{S \cap A \neq \emptyset} m(S)$$

---

# Basic funtions: combination

---

# Algorithm

---

# Available software

| Link           | Language     | Author                       | Comments                                                                                |
|----------------|--------------|------------------------------|-----------------------------------------------------------------------------------------|
| TBM            | MATLAB       | Philippe Smets               | TBM, FMT                                                                                |
| Software       | R and MATLAB | Thierry Denœux               | Clustering, Distance-based Classification, Approximation                                |
| iBelief        | R            | Kuang Zhou and Arnaud Martin | Some basic functions to implement belief functions.                                     |
| Belief Package | R            | Sébastien Destercke          | Some basic functions to deal with discrete belief functions.                            |
| pyds           | Python       | Thomas Reineking             | A Python library for performing calculations in the Dempster-Shafer theory of evidence. |

.footnote[[1] [https://bfasociety.org](https://bfasociety.org)]

---

# New software based on GPU

- Compute the functions in parallel

## Why Python?

- Google Collab

---

# Execution time

---

# Usage

---

# Noelia

piece of code in python

```{python eval=FALSE, include=TRUE}
import numpy as np
import math
a = x + c
math.abs(a)
```

---

# 📨 noeliarico@uniovi.es

What would you like to see in our package?

---